The CrypTool Script: \\ Cryptography, Mathematics and More \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free e-learning program CrypTool\\ (10th edition -- distributed with CrypTool version 1.4.30)} \vspace{60pt}

### 2010-06-02 script/en/script-en.tex
Typos at 2nd page of script in English
New cover of script in English

% Define title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{ % Keine Leerzeilen, sonst Meldung: "Paragraph ended before \title was complete."
	{\Huge The CrypTool Script: \\
	 \vspace{5pt}
	 Cryptography, Mathematics and More} \\
        \vspace{20pt}
	{\LARGE	Background reading\\ 
         for the free e-learning program CrypTool\\
	 (with number theoretic code samples, using Sage)} \\
        \vspace{15pt}
        {\large (10th edition -- distributed with CrypTool version 1.4.30)}
        \vspace{180pt}
}

@@

\includepdf[page=1]{figures/coverv1_en.pdf}    % SR_2009: added new cover

>>>>

% Define title %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{ % Keine Leerzeilen, sonst Meldung: "Paragraph ended before \title was complete."
	{\Huge The CrypTool Script: \\
	 \vspace{5pt}
	 Cryptography, Mathematics, and More} \\
        \vspace{20pt}
	{\LARGE	Background reading for CrypTool\\ 
         the free e-learning program\\
	 (with number theory code samples for Sage)} \\
        \vspace{15pt}
        {\large (10th edition -- distributed with CrypTool version 1.4.30)}
        \vspace{180pt}
}

@@

\includepdf[page=1]{figures/coverv1_en-100dpi.pdf}    % SR_2009: added new cover
